---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)

devtools::load_all()
```

# encuestasmacro

<!-- badges: start -->
[![CI](https://github.com/encuestas-macro/encuestasmacro/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/encuestas-macro/encuestasmacro/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

Tools for processing and analysis of the Macroeconomic Surveys of the Central Bank 
of the Dominican Republic.

## Installation

You can install the development version of `encuestasmacro` with the following command:

```{r, eval=FALSE}
remotes::install_github("encuestas-macro/encuestasmacro")
```

## How to use

In the package you'll find the data of the macroeconomic surveys, as well as functions
to explore and visualized the results. Let's see how we can explore the Macroeconomic
Expectations Survey with the `encuestasmacro` package.

1. Get the data in wide or long format

```{r}
eem_wide <- example_eem_data(format = "wide")
eem_long <- example_eem_data(format = "long")
```

```{r}
head(eem_long)
```

2. Plot the results with the plotting functions

**12 month inflation expectations**
```{r inflacion_interanual_bp, fig.height=4, warning=FALSE}
eem_wide |>
  eem_boxplot(
    variable = "inflacion_interanual",
    font_family = "sans"
  )
```

```{r inflacion_interanual_rbb, fig.height=4, warning=FALSE}
eem_long |>
  eem_ribbon_plot(
    "inflacion",
    font_family = "sans",
    color = colores_em("blue")
  )
```

**Real GDP growth by the end of the year**
```{r gdp_bp, fig.height=4, warning=FALSE}
eem_wide |>
  eem_boxplot(
    variable = "pib_diciembre",
    font_family = "sans",
    color = colores_em("green")
  )
```
